%implementing ocument formatting:
\input{preamble.tex}
\begin{document}
\renewcommand\chaptername{KAPITEL}
\renewcommand\contentsname{Indhold}
\renewcommand\figurename{Figur}
\renewcommand\tablename{Tabel}

\section*{Supervisor meeting\\ \small 10th of September 2015}
\subsection{Study Regulations/Expectations}
\begin{itemize}
\item[-] We do not need to concentrate equally on all subjects.
\item[-] Not all topics in the study regulations needs to be included.
\end{itemize}

\subsection{Main Content in Project}
\begin{itemize}
\item[-] Experts in dynamics! (Differential equations, Laplace transform etc.)
\item[-] Modeling containing deferential equations.
\item[-] Control and communication is not as important as modeling in this project.
\end{itemize}

\subsection{First Things to Do}
\begin{itemize}
\item[-] One of the first things to do is to figure out how the GoT (Games on Track) positioning system works.
\item[-] We need to describe how the GoT positioning system works.
\item[-] Get hardware working.
\end{itemize}

\subsection{Further Remarks}
\begin{itemize}
\item[-] Position control needs to be included on the controller.
\item[-] Delimitation should happen fairly early.
\item[-] Do not make too many requirements - you will not be able to test them.
\item[-] Do not write the requirements before we know enough to put down something specific enough that it is testable (no pseudo requirements!)
\item[-] Make some clear agreements in the group, so everyone is clear on work-flow and methodology.
\end{itemize}

\subsection{Next Supervisor meeting}
Schedule by mail.

\end{document}

% TEGN
%-----------------------------
% Højrepil:		$\rightarrow$